Testing atlantisom: generate census length comps

### 2019-05-08 TrueLengthCompTest.Rmd
save this, if it ever returns
trying for atf only

So, test 1 is running `calc_age2length` with the full true dataset. This should work because there will be no aggregation of the output:

```{r calcage2length-truth, warning=FALSE, message=FALSE, eval=FALSE}

@@

length_census <- calc_age2length(structn = truth$structn,
                                 resn = truth$resn,
                                 nums = truth$nums,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

This produces output, after a looooooong time. Its doing it for all species, which is a problem. Visualize a tiny bit:

@@

atf_length_census <- length_census$natlength %>%
  filter(species %in% ("Arrowtooth_flounder"))

@@

It should save time to run the census survey to get true length comps, because at least it aggregates over polygon and layer. Test this:

>>>>

So, test 1 is running `calc_age2length` with the full true dataset. This should work because there will be no aggregation of the output (no, don't do this with the full dataset! example with one species instead):

```{r calcage2length-truth, warning=FALSE, message=FALSE}

@@

# length_census <- calc_age2length(structn = truth$structn,
#                                  resn = truth$resn,
#                                  nums = truth$nums,
#                                  biolprm = truth$biolprm, fgs = truth$fgs,
#                                  CVlenage = 0.1, remove.zeroes=TRUE)
# 
# # never got here with full truth
# saveRDS(length_census, file.path(d.name, paste0(scenario.name, "length_census.rds")))

# try for a single species
# everyone's favorite predator
atf_truestructn <- truth$structn[truth$structn$species == "Arrowtooth_flounder",]
atf_trueresn <- truth$resn[truth$resn$species == "Arrowtooth_flounder",] 
atf_truenums <- truth$nums[truth$nums$species == "Arrowtooth_flounder",]

atf_length_census <- calc_age2length(structn = atf_truestructn,
                                 resn = atf_trueresn,
                                 nums = atf_truenums,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

This produced output for a single species by mistake. It ran for hours on the full truth dataset and did not complete (I stopped it). Its doing it for all species, which is a problem. Rewrote for just one species to see full length comp by area and depth layer.

Visualize a tiny bit:

@@

@@

Try again with survey sampling for nums, structn and resn, which limits the species list to fish and sharks, and also aggregates over layer and polygon. Test this:
